Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-11 paper.tex
on lukas question: prefer to discuss about collective behaviour instead of distributed (or decentralised) collective intellingence

\section{Background and Motivation}
\label{sec:background}
In this section, we aim to provide a concise overview of the system we intend to address, 
 starting with a high-level system model. 
%
We then proceed to discuss relevant research areas that inform our approach. 
%
Finally, we present a formalization of the problem and a discussion of the motivations behind our proposed work.
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Swarm systems}
This article focuses on the definition of \emph{decentralised collective intelligence} within the context of \emph{large-scale} distributed systems.
 Specifically, we focus on \emph{Cyber-Physical Swarms} or \emph{swarm-like systems}, i.e.,  systems consisting of \emph{devices} (or nodes) equipped with \emph{sensors} and \emph{actuator} able to interact with the real world.
 Each of these nodes can interact with its direct neighbours, either based on physical (e.g. communication range) or logical distance (e.g. 1-hop neighbourhood).
 \lukas{does the article focus on the definition of decentralised collective intelligence?}
  \lukas{distributed or decentralised?}

>>>>

\section{Background and Motivation}
\label{sec:background}
In this section, we aim to provide a concise overview of the system we intend to address, 
 starting with a high-level system model. 
%
We then proceed to discuss relevant research areas that inform our approach. 
%
Finally, we present a formalization of the problem and a discussion of the motivations behind our proposed work.
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Swarm systems}
This article aims in defining intelligent \emph{collective behaviours} within the context of \emph{large-scale} distributed systems.
 Specifically, we focus on \emph{Cyber-Physical Swarms} or \emph{swarm-like systems}, i.e.,  systems consisting of \emph{devices} (or nodes) equipped with \emph{sensors} and \emph{actuator} able to interact with the real world.
 Each of these nodes can interact with its direct neighbours, either based on physical (e.g. communication range) or logical distance (e.g. 1-hop neighbourhood).
 %\lukas{does the article focus on the definition of decentralised collective intelligence?}
 % \lukas{distributed or decentralised?}
